Memo fractal dimension

### 2014-12-17 2014_12_16_memo_fractal.tex
Generation of the graph by empirical_fractal.py Inverse circles and lines, less circles.

\begin{figure}
\includegraphics{empirical_fractal}
\caption{Testing empirical expression. Lines are numerical integration of (Eq.~\ref{eq:exact}) normalized by $2\Gamma(d)$ for $d=1,1.5,2$. Circles are the corresponding empirical expression.}
\label{fig:empirical}
\end{figure}

>>>>

\begin{figure}
\includegraphics{empirical_fractal}
\caption{Testing empirical expression. Circles are numerical integration of (Eq.~\ref{eq:exact}) normalized by $2\Gamma(d)$ for $d=1,1.5,2$. Lines are the corresponding empirical expression.}
\label{fig:empirical}
\end{figure}
